The pollination trade-off

### 2018-12-01 paper/manuscript.Rmd
Show number of contrasting species for conspecific pollen criteria too

# species with both positive and negative relationships
sp_both_pos_neg <- facilitation_plot_df %>%
  dplyr::filter(effect_category != "neutral") %>%
  dplyr::group_by(plant_name) %>%
  dplyr::summarise(both = dplyr::n_distinct(effect_category) > 1) %>%
  dplyr::filter(both)

@@

sp_con_con <- con_con_plot_df %>%
  dplyr::group_by(effect_category) %>%
  dplyr::count() %>%
  dplyr::group_by() %>%
  dplyr::mutate(np = n/sum(n), 
                np = round_preserve_sum(np, 2)*100)
```

We then compared the amount of conspecific pollen deposited on flowers open to animal-mediated pollinators and those that were closed. 
We found that generally, most species had more conspecific pollen deposited in their stigmas when animal-mediated pollination took place, although for most species the difference was not significant at the 0.05 level (Mann-Withney U tests; Figure \@ref(fig:fig-trade-off-predictions)c). 
Specifically, the difference weas non-signifcant for `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`% of species in a community, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% had significantly more pollen when open, and the remaining `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had significantly less pollen when open.

>>>>

# species with both positive and negative relationships
get_sp_with_both_pos_neg <- . %>%
  dplyr::filter(effect_category != "neutral") %>%
  dplyr::group_by(plant_name) %>%
  dplyr::summarise(both = dplyr::n_distinct(effect_category) > 1) %>%
  dplyr::filter(both)
sp_both_pos_neg <- facilitation_plot_df %>%
  get_sp_with_both_pos_neg()

@@

sp_con_con <- con_con_plot_df %>%
  dplyr::group_by(effect_category) %>%
  dplyr::count() %>%
  dplyr::group_by() %>%
  dplyr::mutate(np = n/sum(n), 
                np = round_preserve_sum(np, 2)*100)
# species with contrasting behaviours
sp_con_both_pos_neg <- con_con_plot_df %>%
  get_sp_with_both_pos_neg()
```

We then compared the amount of conspecific pollen deposited on flowers open to animal-mediated pollinators and those that were closed. 
We found that generally, most species had more conspecific pollen deposited in their stigmas when animal-mediated pollination took place, although for most species the difference was not significant at the 0.05 level (Mann-Withney U tests; Figure \@ref(fig:fig-trade-off-predictions)c). 
Specifically, the difference weas non-signifcant for `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`% of species in a community, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% had significantly more pollen when open, and the remaining `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had significantly less pollen when open. 
Variation within species was slightly smaller and only `r numbers2words(nrow(sp_con_both_pos_neg))` species (*H. incana* and *C. acanthoides*) had both significantly positive and negative differences.
